\addcontentsline{toc}{chapter}{参考文献}	% 目次への項目表示
\begin{thebibliography}{99}
\bibitem{corona}
飯田，森本，福留，三好，宇佐川，空間音響学，コロナ社，2010 

\bibitem{bochum}
Markus Bodden, "Binaural Modeling and Auditory Scene Analysis, "
IEEE 1995 Workshop on Applications of Signal Processing to Audio and Acoustics, 
Mohonk Mountain House(New Paltz, NY), 1995.

\bibitem{fdbm}
H. Nakashima, Y. Chisaki, T. Usagawa, “Frequency domain
binaural model based on interaural phase and level
difference, “ Acoustical Science and Technology, Vol. 24，
No. 4, pp.172-178, 2003.

\bibitem{hrtf}
K. Iida, M. Itoh, M. Morimoto, “Median plane localization
using a parametric model of the head-related transfer
function based on spectral cues, ” Applied Acoustics, Vol. 
68, pp.835-850, 2007.

\bibitem{nn}
今村 浩二郎, 苣木 禎史, 宇佐川 毅, “両耳信号を用いた
矢状面座標に基づく音源方向推定 -象限分割による方向
推定精度向上について-, ” 電子情報通信学会技術研究
報告, Vol.68, No.286, EA2009-85, pp.55-60, 2009.

\bibitem{cue}
佐保 貴哉, 苣木 禎史, 宇佐川 毅, “周波数領域両耳聴モ
デルに基づく補聴システムにおける前後誤判断の抑制手
法, ” 電子情報 通信学会 技術 研究報告, Vol. 111, No. 
175, EA2011-56, pp.37-42

\bibitem{yoshino}
S. Yoshino, T. Tomita, Y. Chisaki, T. Usagawa, "On a Binaural Model with 
Front-back Discriminator using Artificial Neural Network trained by multiple
 HRTF catalogs, " 43rd International Congress on Noise Control Engineering, 2014.

\bibitem{deep_learning}
岡谷貴之, "機械学習プロフェッショナルシリーズ 深層学習, " 
講談社, 2015.

\bibitem{imamura}
K. Imamura, Y. Chisaki, T. Usagawa, "An estimation method
of sound source direction in sagittal coordinate utilizing
binaural input, " Proc. YKJCA(Youngnam-Kusyu Joint Conference on Acoustics)
, pp.111-114, 2009.

\bibitem{tomita}
富田 拓郎, "周波数領域両耳聴モデルにおける前後判断機能実装に関する研究, "
熊本大学大学院自然科学研究科情報電気電子工学専攻 修士論文, 2014.

\bibitem{tensorflow}
Nick McClure, “TensorFlow 機械学習クックブック, ” 
株式会社インプレス, 2017.

\bibitem{batch_size}
Nitish Shirish Keskar, Dheevatsa Mudigere, Jorge Nocedal, Mikhail Smelyanskiy, Ping Tak Peter Tang, 
"ON LARGE-BATCH TRAINING FOR DEEP LEARNING: GENERALIZATION GAP AND SHARP MINIMA, "
ICLR 2017, 2017.

\bibitem{tinkerboard}
Tinker Board Single-board Computer ASUS United Kingdom : https://www.asus.com/uk/Single-Board-Computer/Tinker-Board/

\bibitem{30ms}
T. Kurita, S. Iai, N. Kitawaki, "Effects of Transmission Delay in Audiovisual Communication, " IEICE, Vol. J76-B-I, No.4, pp.331-339, 1993.

\bibitem{kiyota}
清田 佳偉, イルワンシャー, 松岡 光佑,　宇佐川 毅, "周波数領域両耳聴モデルを用いた複数話者同時発話時の話者識別に関する研究, " 電子情報通信学会技術研究報告 Vol. 118 No. 410, 2019.

\end{thebibliography}


